Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-15 PAPER.tex
changed optimal weighting case to 2% Tr(C) instead of 4%

\subsubsection{Signal Loss Methodology} 
\label{sec:siglossmethod}
In short, our method consists of adding an EoR-like signal into the data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.  To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ 
cm signal visibilities. Here we use the same method as in \citetalias{ali_et_al2015}, where mock Gaussian noise visibilities (mock EoR signals) 
are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.\footnote{One 
specific change from \citetalias{ali_et_al2015} is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
estimate of signal loss, %(by a factor of $\sim$$10$), 
likely due to the use of the fringe-rate filter as a simulator. However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in \citetalias{ali_et_al2015} (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}

@@

The quantity $P_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$. Since there is no noise contribution to $\mathbf{e}$, it can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations. The role of $P_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics. This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments. In principle, one could compute $P_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline. In practice, however, such simulations may not accurately reflect real-life systematics and foregrounds. To overcome this obstacle, one can make the assumption that since the EoR signal is expected to be small, the data vector $\mathbf{x}$ itself is our best model of these contaminants. Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.

@@

{\bf Small injection:}
%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$. They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected. 
%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples. Output values are gaussian distributed around zero, spanning a range of values set by the injection level. This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below). In fact, for the unweighted case, the cross term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a gaussian with zero mean and width $\sqrt{p_e}\sqrt{p_x}$. %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term. However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$. It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black). We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).

{\bf Large injection:}
When the injected signal is much larger than the measured power spectrum, the data-only components can 
be neglected as many orders of magnitude smaller. This regime is somewhat academic given that, in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than a cosmological signal.  However it is useful as a check of our system in a relatively simple case.   As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms are small in comparison to the signal-only term. Here only does the signal-only term used in  \citetalias{ali_et_al2015} dominate the total power output. We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean). This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$. The cross correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}$.

{\bf In between:}
When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
the weighted injected power spectrum component mirrors the input power indicating little loss (i.e. the green curve follows the dotted black line), eventually 
departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
the cross-term has nearly the same amplitude, but with a negative sign. As explained below, this negativity is the result of cross correlating inverse covariance weighted things.  This negative component drives down the $P_{\rm out}$ estimator (black). We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data level. Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in \citetalias{ali_et_al2015}.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
	\caption{Illustration of the power spectrum amplitude as a function of injected power level summed into the 
data. The net output ($P_{out}=P_r$) is shown in black, the individual cross terms, as defined by Equation 
\eqref{eq:crossterm},  are shown in blue, red, green; the dotted line indicates 1:1 input to output mapping.  The 
empirical inverse covariance weighted case used in \citealt{ali_et_al2015} is on the left and uniform-weighted 
case on the right. The details of the simulation used to generate the figure is explained in Section 
\ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.   The gray 
line is the power spectrum value of data alone (doesn't depend on injected power). The green signal-signal 
component is also the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
than the net output because the cross terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
regime where cross correlation between injection and data are not dominant, the cross-terms have a noise-like 
term with width $\sqrt{P_e}$. However, at power levels comparable to the data (the middle region), the cross-
terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect 
$\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for 
the empirical inverse covariance weighted case). }
	\label{fig:sigloss_terms}
\end{figure*}

@@

\noindent where we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
an eigenbasis of $\textbf{e}$, so that $\langle 
\textbf{ee}^{\dagger} \rangle_{t}$ is diagonal. The middle 
two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}\footnote{This same appendix also gives a now-prescient warning about signal loss and the dangers of noise and sample variance in inverse covariance.}, to leading order the inversion of a diagonal-dominant matrix like $\widehat{\textbf{C}}_{r}$ (from $\langle 
\textbf{ee}^{\dagger} \rangle_{t}$) with smaller
off-diagonal terms results in a new diagonal-dominant matrix with negative off-diagonal terms. These off-diagonal
terms depend on both $\textbf{x}$ and $\textbf{e}$. Then, when $\widehat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
the result is a vector that is similar to $\textbf{x}$ but
contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\widehat{\textbf{C}}^{-1}_{r}$. The
correlation is negative because the product $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
of the off-diagonal terms in $\widehat{\textbf{C}}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
of a diagonal-dominant matrix.
% XXX [ARP: we may want to write this all out explicitly in an appendix]

%The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
%simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data. Therefore, in our revised 
%signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
%weighted power spectrum of the data from the weighted power spectrum of data plus EoR.

@@

{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator is that it is not properly normalized.  Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data. However, the normalization matrix $\mathbf{M}$ is derived assuming that the unnormalized estimator is quadratic in the data.  The power spectrum estimate will also be incorrectly normalized which manifests as signal loss. We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss, and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics

@@

One issue to address is how one incorporates the randomness of $P_{\rm out}$ into our signal loss corrections. A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e. cosmic variance) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e. how much coupling there is, which affects how much loss results).

Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$.  Bayes' rule relates the posterior, which we don't know, to the reverse probability, which we do know, in other words,

\begin{equation}
\label{eq:Bayes}
p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})},
  p(P_{\rm in}) ,
\end{equation}

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.png}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. full inverse 
covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using empirical inverse covariance weighting. Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance. This regularization knob is tuned from $0\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e. empirical inverse covariance weighting) to $20\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left. Also 
plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (dashed blue) and inverse variance 
weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green. In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
	\label{fig:sigloss_modeloop}
\end{figure*}

In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
in both panels and represents a third regularization technique. This line (red) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity 
matrix element-wise to $\widehat{\textbf{C}}$). This result is single-valued and not a function of the x-axes. We see that all three regularization schemes shown (black solid, black dashed, red) perform similarly at 
their best (i.e. when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black solid curve). However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.04Tr(\widehat{\textbf{C}})$, which we will denote as $\widehat{\textbf{C}}_{eff}$. We choose this weighting scheme because it slightly out-performs the other weighting schemes, likely due to the fact that it retains information from all eigenmodes (i.e. it doesn't throw away some information as in the other cases) but re-weights them in a way that produces minimal loss.

A revised PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{eff}$) is shown in Figure 
\ref{fig:ps1_data}. Again, black and gray points correspond to positive and negative power spectrum values respectively, with 
$2\sigma$ errors bars. Also plotted are the uniform-weighted power spectrum upper limit (dashed blue) and theoretical prediction of 
noise (solid green). In Kolopanis et al., (\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$, 
a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.

>>>>

\subsubsection{Signal Loss Methodology} 
\label{sec:siglossmethod}
In short, our method consists of injecting an EoR-like signal into the data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.  To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ 
cm signal visibilities. Here we use the same method as in \citetalias{ali_et_al2015}, where mock Gaussian noise visibilities (mock EoR signals) 
are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.\footnote{One 
specific change from \citetalias{ali_et_al2015} is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
estimate of signal loss, %(by a factor of $\sim$$10$), 
likely due to the use of the fringe-rate filter as a simulator. However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in \citetalias{ali_et_al2015} (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}

@@

The quantity $P_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$. Since there is no noise contribution to $\mathbf{e}$, it can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations. The role of $P_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics. This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is outputted by our analysis pipeline prior to any signal loss adjustments. In principle, one could compute $P_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline. In practice, however, such simulations may not accurately reflect real-life systematics and foregrounds. To overcome this obstacle, one can make the assumption that since the EoR signal is expected to be small, the data vector $\mathbf{x}$ itself is our best model of these contaminants. Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.

@@

{\bf Small injection:}
In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$. They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected. This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. In this regime, we also note that the cross-terms (red) behave as noise, even in the empirically inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below)%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term. However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$. It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black). We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).

{\bf Large injection:}
When the injected signal (red) is much larger than the data-only power spectrum (gray), the data-only components can 
be neglected as many orders of magnitude smaller. As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are also small in comparison to the signal-only term (green). Here only does the signal-only term recover the ``loss'' injected simulated EoR signal as intended (i.e. the black and green curves agree). We again see that the cross-terms behave as noise at large injections in the empirical inverse covariance weighted case for a similar reasoning as it does at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$, avoiding correlations with $\textbf{x}$.

{\bf In between:}
When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
the weighted injected power spectrum component mirrors the input power indicating little loss (i.e. the green curve follows the dotted black line), eventually 
departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
the cross-terms have nearly the same amplitude, but with a negative sign. The sum of the two is substantially lower and therefore drives down the $P_{\rm out}$ estimator (black). We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data level. Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in \citetalias{ali_et_al2015}.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
	\caption{Illustration of the power spectrum components used to estimate signal loss, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the empirical inverse covariance weighted case (left) and uniform-weighted case (right). The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we fit smooth polynomials to our data points to create the curves. We show the contributions of three signal loss terms (blue, red, green), which when combined via Equation \eqref{eq:crossterm} produce the black curve ($\widehat{\textbf{p}}_{r}$). The gray curve is the power spectrum value of data alone. Most notably, the green curves (the signal-only term) denotes the signal loss analysis used in \citetalias{ali_et_al2015}, and the red curves showcase the importance of the cross-terms in computing signal loss. As explained in the main text, the cross-terms behave as noise (with some range of values), for very small and large injection levels. For the empirical inverse covariance weighted case, it is in these extreme regimes when $\widehat{\textbf{C}}_{r}$ is dominated by either $\textbf{x}$ (low injects) or $\textbf{e}$ (large injects). However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the empirical inverse covariance weighted case). Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the uniform-weighted case.}
	\label{fig:sigloss_terms}
\end{figure*}

@@

\noindent where we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
an eigenbasis of $\textbf{e}$, so that $\langle 
\textbf{ee}^{\dagger} \rangle_{t}$ is diagonal. The middle 
two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}, to leading order the inversion of a matrix like $\widehat{\textbf{C}}_{r}$ that is diagonal-dominant (from $\langle 
\textbf{ee}^{\dagger} \rangle_{t}$) with smaller
off-diagonal terms results in a new diagonal-dominant matrix with negative off-diagonal terms. These off-diagonal
terms depend on both $\textbf{x}$ and $\textbf{e}$. Then, when $\widehat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
the result is a vector that is similar to $\textbf{x}$ but
contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\widehat{\textbf{C}}^{-1}_{r}$. The
correlation is negative because the product $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
of the off-diagonal terms in $\widehat{\textbf{C}}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
of a diagonal-dominant matrix.
% XXX [ARP: we may want to write this all out explicitly in an appendix]

The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data. Therefore, in our revised 
signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
weighted power spectrum of the data from the weighted power spectrum of data plus EoR.

@@

{\bf In general:} Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data. However, the normalization matrix $\mathbf{M}$ is generally derived assuming that the unnormalized estimator is quadratic in the data. Thus, neglecting couplings between data and its weightings causes power spectrum estimates to be incorrectly normalized. As argued in this section, the resulting bias will tend to bias the results \emph{low}, which is simply another way of describing signal loss.

@@

One issue to address is how one incorporates the randomness of $P_{\rm out}$ into our signal loss corrections. A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e. behaves like noise) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e. how much coupling there is, which affects how much loss results).

Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$. Bayes' rule gives

\begin{equation}
\label{eq:Bayes}
p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})}
  p(P_{\rm in}) ,
\end{equation}

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.png}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. full inverse 
covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using empirical inverse covariance weighting. Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance. This regularization knob is tuned from $0\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e. empirical inverse covariance weighting) to $20\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left. Also 
plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (dashed blue) and inverse variance 
weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green. In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.02Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
	\label{fig:sigloss_modeloop}
\end{figure*}

In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
in both panels and represents a third regularization technique. This line (red) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity 
matrix element-wise to $\widehat{\textbf{C}}$). This result is single-valued and not a function of the x-axes. We see that all three regularization schemes shown (black solid, black dashed, red) perform similarly at 
their best (i.e. when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black solid curve). However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.02Tr(\widehat{\textbf{C}})$, which we will denote as $\widehat{\textbf{C}}_{eff}$. We choose this weighting scheme because it slightly out-performs the other weighting schemes, likely due to the fact that it retains information from all eigenmodes (i.e. it doesn't throw away some information as in the other cases) but re-weights them in a way that produces minimal loss. In this paper, we use this weighting scheme as a simple regularization demonstration, though we note that in Kolopanis et al., (\textit{submitted}) we choose the most optimal regularization parameter for our final limits.

A revised PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{eff}$) is shown in Figure 
\ref{fig:ps1_data}. Again, the dashed black curve represents our upper limit on EoR, post-signal loss estimation. Black and gray points correspond to positive and negative power spectrum values respectively (pre-signal loss estimation), with 
$2\sigma$ errors bars. Also plotted are the uniform-weighted power spectrum upper limit (dashed blue) and theoretical prediction of 
noise (solid green). In Kolopanis et al., (\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$, 
a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.
